% Emacs, this is -*-latex-*-

\title{\href{https://github.com/vicente-gonzalez-ruiz/MCTF}{Motion Compensated Temporal Filtering}}

\maketitle

\section{Idea and notation}
%{{{

MCTF is a DWT where the input samples are the original video images
and the output is a sequence of residue images.

Motion Compensated Temporal Filtering (MCTF)~\cite{ohm1994three}
inputs two or more frames of pixels\footnote{Although the frames can
  also be in a transform domain, such as the DWT domain.} and outputs
two or more frames of coefficients. Some of these frame-coeffs contain
low frequency information (in the temporal domain), and others
represent high frequency temporal information. We will use
\emph{average}-frame (or simply \emph{average}) to refer to a
low-frequency frame, and \emph{residue} to refer to a high-frequency
frame. In general, the number of averages is smaller tha the name of
residues.

%}}}

\section{Objectives of MCTF}
%{{{

The main goals of
\href{https://en.wikipedia.org/wiki/Motion_compensation}{motion
  compensation} are:
\begin{enumerate}
\item Reduce the entropy of the residuals, and if
\item Increase the temporal scalability, compared to low-delay and
  random-access modes~\cite{vruiz__sistemas_multimedia}. MCTF is a
  dyadic temporal multirresolution approach.
\end{enumerate}
  
%}}}

\section{MCTF uses ME}
%{{{

In order to exploit the temporal redundancy, the bidirectional
predictions used in MCTF are generated using ME (Motion
Estimation)~\cite{vruiz__ME}. The motion information (usually in the
form of motion vector fields with a given density\footnote{Number of
  motion vectors per pixel.}) must be known by both, the encoder and
the decoder, which runs the inverse MCTF. Therefore, MCTF can be
considered an adaptive transform, and, as many others adaptive
systems, the side information must be transmitted to or regenerated by
the decoder.

%}}}

\section{(Expected) Entropies and  dynamic ranges}
%{{{

Usually, MCTF (as many other transforms), increases the number of bits
necessary to represent the residues (coefficients), but also decreases
the entropy, because most of the information will be concentrated in a
small number of residues~\cite{vruiz__MEC}.

%}}}

\section{References}
%{{{

\renewcommand{\addcontentsline}[3]{}% Remove functionality of \addcontentsline
\bibliography{image_pyramids,DWT,motion_estimation,HEVC}

%}}}
